Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-28 sections/approach.tex

Our goal is to improve the efficiency and confidence in determining the usefulness of review comments. As discussed previously, this is largely based on relevance the comment has to the proposed change (as documented within a MCR system). According to relevance theory, a primary factor in relevance is similarly, and so it is natural for us to consider classification \emph{similarity conditions}. 
\dan{can we find a reference for relevance and similarly?}
That is, we assume that that the more similar a comment is to the proposed change, the more relevant it is and hence more likely useful. Conversely, the more dissimilar\footnote{This can be arbitrarily large, thus not simply the opposite of similarity} , the less relevant, and hence less useful. Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification. That is, for some degree of similarity a comment is most likely useful, and for some degree of dissimilarity it is most likely not useful. The key is determining these degrees in a practical and effective manner. While this representation is straightforward and automatically adjusts ti the quality of the data, it has a few drawbacks. First, we have to accept that some comments cannot be reliably or confidently classified. We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} i.e. unable to assess (subjectively) comment usefulness. Again, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets. This decreases the cost-effectiveness limiting the practicality of application to projects with a large enough number of comments whee the classification effort saved overcomes the training costs.  
% empirically driven and automatically adapts to the quality the data
 Fig. \ref{fig:overview} shows an overview of our proposed classification approach.
Usefulness of a comment is determined by computing its semantic similarity with the commit message of proposed change and observing if it satisfies \emph{usefulness classification likelihood conditions}. The conditions are simply threshold values of similarity and dissimilarity empirically determined to optimize a desired likelihood objectives. In our case example we chose to maximize the F-measure, but other likelihood functions could be used depending on precision, recall, or risk goals.    
To calculate semantic similarity Fig. \ref{fig:overview}(a), we used the Vector Space Model (VSM) with the cosine distance measure which is a well-known technique for retrieving similar documents written in unstructured natural language. 
The Euclidian distance is a well-established measure of dissimilarity and applies analogously.
%For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig. \ref{fig:overview}(b). \thai{The %overview figure does not have (a) and (b)...}
%\dan{what was the actual effort (in person-hours) to create the training data?}
The training data is a small set of randomly-selected pairs of comments and corresponding commit messages are manually assessed for usefulness. For statistical purposes at least 30 useful and 30 useless comments are needed. The similarity and dissimilarities are computed for the data set. These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that can best (relative to some likelihood function such as F-measure) discriminate useful comments and $S'_T$ and $D'_T$ for useless comments. Using these thresholds, we can classify the usefulness of comments for the rest of comments in review history according to the classification model as follows:
\begin{itemize}
\item \textbf{useful}: $\Theta(c,m,S_T,D_T) = \True$ iff $\Sim(m,c) \geq S_T$ and $\Dist(m,c) \leq D_T$.
\item \textbf{useless}: $\Omega(c,m,S'_T,D'_T) = \True$ iff $\Sim(m,c) \leq  S'_T$ and $\Dist(m,c) \geq D'_T$.
\item \textbf{undetermined}: Neither of the above conditions are $\True$.
\end{itemize}

@@

The details of our approach are elaborated in the following subsections.

@@

We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that maximize $\mathrm{F\text{-}measure}_{s_t,d_t}$ Equation \ref{eq:fmeasure}. This is a performance measurement for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).

The F-measure for $\Omega(c,S_T=s_t,D_T=d_t)$ is computed analogously where we change instances of useful to useless and vice-versa in the definitions. The correctness of classification is determined from the useful/useless defined dataset.

>>>>

Our goal is to improve the efficiency and confidence in determining the usefulness of review comments.
As discussed previously, this is largely based on relevance the comment has to the proposed change (as documented within a MCR system).
According to relevance theory, a primary factor in relevance is similarly, and so it is natural for us to consider classification using \emph{similarity conditions}. 
\dan{can we find a reference for relevance and similarly?}

That is, we assume that that the more similar a comment is to the proposed change, the more relevant it is and hence more likely useful.
Conversely, the more dissimilar\footnote{This can be arbitrarily large, thus not simply the opposite of similarity}, the less relevant, and hence less useful.

Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification.
That is, for some degree of similarity a comment is most likely useful, and for some degree of dissimilarity it is most likely not useful.
The key is determining these degrees in a practical and effective manner.
While this representation is straightforward and automatically adjusts to the quality of the data, it has a few drawbacks.

First, we have to accept that some comments cannot be reliably or confidently classified.
We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} (i.e. cannot be assessed subjectively).
Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.  
% empirically driven and automatically adapts to the quality the data

Fig. \ref{fig:overview} shows an overview of our proposed classification approach.
Usefulness of a comment is determined by computing its semantic similarity with the commit message of proposed change and observing if it satisfies \emph{usefulness classification likelihood conditions}.
The conditions are simply threshold values of similarity and dissimilarity empirically determined to optimize a desired likelihood objectives.
In our case example we chose to maximize the F-measure, but other likelihood functions could be used depending on precision, recall, or risk goals.

% again, I can't see Fig. \ref{fig:overview}(a)
% Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
To calculate semantic similarity, we used the Vector Space Model (VSM) with the cosine similarity measure, which is a well-known technique for retrieving similar documents written in unstructured natural language; and the Euclidian distance, which is a well-established measure of dissimilarity and applies analogously.
%For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig. \ref{fig:overview}(b). \thai{The %overview figure does not have (a) and (b)...}
%\dan{what was the actual effort (in person-hours) to create the training data?}

Our training data is a small set of randomly-selected pairs of comments and the corresponding commit messages.
These comments are manually assessed for usefulness.
For statistical purposes, at least 30 useful and 30 useless comments must be collected.
The similarity and dissimilarities are then computed for the data set.
These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that can best (relative to some likelihood function such as F-measure) discriminate useful comments and $S'_T$ and $D'_T$ for useless comments.

Using these thresholds, we can classify the usefulness of comments for the rest of comments in review history according to the classification model as follows: given a comment $c$ and a corresponding commit message $m$,
\begin{itemize}
\item \textbf{useful}: $\Theta(c,m,S_T,D_T) = \True$ iff $\Sim(m,c) \geq S_T$ and $\Dist(m,c) \leq D_T$.
\item \textbf{useless}: $\Omega(c,m,S'_T,D'_T) = \True$ iff $\Sim(m,c) \leq  S'_T$ and $\Dist(m,c) \geq D'_T$.
\item \textbf{undetermined}: neither or both of the above conditions are $\True$.
% We also refer to them as \emph{neither} and \emph{overlap}.
\end{itemize}

@@

% The details of our approach are elaborated in the following subsections.

@@

We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that maximize the F-measure,
which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).

In this paper, we used the F$_1$ measure, which gives equal weight to both precision and recall.
Depending on application, different weights can be given by choosing a different F$_\beta$ measure.

% Thai sez: We did not mention the F-measure for \Theta, thus suddenly referring to \Omega does not make much sense...
% The F-measure for $\Omega(c,S_T=s_t,D_T=d_t)$ is computed analogously where we change instances of useful to useless and vice-versa in the definitions. The correctness of classification is determined from the useful/useless defined dataset.
